### 2020-05-08 ncov.tex
tomorrow

Finally, \fref{R0} compares the base estimates (based on $r_i$, $\bar G_i$, and $\kappa_i$ for each study $i$) and 21 substitute estimates (3 parameter substitutions $\times$ 7 studies).
All but 8 substitute estimates have wider credible intervals compared to their corresponding base estimates --- namely, $\bar G$-substitute estimates for Study 1 and 7, $r$-substitute estimates for Study 1 and 2, and  $\kappa$-substitute estimates for Study 3, 6, and 7.
Furthermore, accounting for uncertainties in the estimate of $r$ has the largest effect on the estimates of \Ro\ in most cases (\fref{R0}).
For example, the $r$-substitute estimate of \Ro for Study 7 is $\Ro = 3.9$ (95\% CI: 2.3--8.8), which is much wider than the uncertainty range they reported (2.0--3.1).
This is consistent with our earlier results (\fref{eff}) that demonstrated the importance of accounting for uncertainty in the exponential growth rate $r$.
We also note that the pooled estimate of the basic reproductive number ($\Rpool = 3.0$; 95\% CI: 2.1--4.6) has wider credible intervals than the base estimates except for Study 2.

>>>>

Finally, \fref{R0} compares the base estimates (based on $r_i$, $\bar G_i$, and $\kappa_i$ for each study $i$) and 21 substitute estimates (3 parameter substitutions $\times$ 7 studies).
All but 8 substitute estimates have wider credible intervals compared to their corresponding base estimates --- namely, $\bar G$-substitute estimates for Study 1 and 7, $r$-substitute estimates for Study 1 and 2, and  $\kappa$-substitute estimates for Study 3, 6, and 7.
Furthermore, accounting for uncertainties in the estimate of $r$ has the largest effect on the estimates of \Ro\ in most cases (\fref{R0}).
For example, the $r$-substitute estimate of \Ro for Study 7 is $\Ro = 3.9$ (95\% CI: 2.3--8.8), which is much wider than the uncertainty range they reported (2.0--3.1).
This is consistent with our earlier results (\fref{eff}) that demonstrated the importance of accounting for uncertainty in the exponential growth rate $r$.
We also note that the pooled estimate of the basic reproductive number ($\Rpool = 3.0$; 95\% CI: 2.1--4.6) has wider credible intervals than the base estimates except for Study 6.
